
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# builddeps

> Find Build-Time Package Dependencies

[![Linux Build Status](https://travis-ci.org//builddeps.svg?branch=master)](https://travis-ci.org//builddeps)

[![Windows Build status](https://ci.appveyor.com/api/projects/status/github//builddeps?svg=true)](https://ci.appveyor.com/project//builddeps)
[![](http://www.r-pkg.org/badges/version/builddeps)](http://www.r-pkg.org/pkg/builddeps)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/builddeps)](http://www.r-pkg.org/pkg/builddeps)


Most R package dependencies are run-time dependencies: functions within a
  package refer to functions or other objects within another package. These
  references are resolved at runtime, and for evaluating the code of a package
  (i.e. installing it), the dependencies are not actually needed. This package
  tries to work out the build-time and run-time dependencies of a package, by
  trying to evaluate the package code both without and with each dependency.

## Installation

```{r eval = FALSE}
devtools::install_github("/builddeps")
```

## Usage

```{r}
library(builddeps)
```

## License

MIT + file LICENSE © 
